Validating Cell Tower Clustering for Mobility Prediction

### 2012-12-12 docs/paper589.tex
typo

\xxx{Compare MDC and Reality Mining, i.e. show that they are similiar using the sampled RM?}

@@

\paragraph{Cluster incompleteness} For a cell $k$, this is the number of cells within $\delta_{incomp}$ meters of it that are not in the same cluster as $k$. The algorithm is shown in \xxx{Show the cluster incompleteness algorithm.} Intuitively this measures if there are potentially oscillating towers that are not being clustered together. We can think of the cluster incompleteness as the dual of the cluster distance: the former favors agressive algorithms while the latter encourages conservative approaches. Another way to see the benefit of using two metrics is noting that there are trivial solutions that minimize distance or incompleteness (each cell in its own cluster and one huge cluster with all cels, respectively), but there are no trivial solutions that minimize both metrics at the same time.

@@

In order to provide some confidence in the precision of the results, we only consider cells that were seen more than once in the GPS logs, with a standard deviation less than 500 meters. Only clusters in which more tha 70\% of cells meet this criteria are analyzed. This meant that only 82 clusters, or 9.44\% of the total, could be analyzed. Although this is a small fraction, there is no reason to think it is a biased sample if we assume there is no correlation between GPS precision and clustering ineffiency. Therefore, the results should hold for the entirety of the clusters, and, we conjecture, for other datasets too.

>>>>

\xxx{Compare MDC and Reality Mining, i.e. show that they are similar using the sampled RM?}

@@

\paragraph{Cluster incompleteness} For a cell $k$, this is the number of cells within $\delta_{incomp}$ meters of it that are not in the same cluster as $k$. The algorithm is shown in \xxx{Show the cluster incompleteness algorithm.} Intuitively this measures if there are potentially oscillating towers that are not being clustered together. We can think of the cluster incompleteness as the dual of the cluster distance: the former favors aggressive algorithms while the latter encourages conservative approaches. Another way to see the benefit of using two metrics is noting that there are trivial solutions that minimize distance or incompleteness (each cell in its own cluster and one huge cluster with all cels, respectively), but there are no trivial solutions that minimize both metrics at the same time.

@@

In order to provide some confidence in the precision of the results, we only consider cells that were seen more than once in the GPS logs, with a standard deviation less than 500 meters. Only clusters in which more tha 70\% of cells meet this criteria are analyzed. This meant that only 82 clusters, or 9.44\% of the total, could be analyzed. Although this is a small fraction, there is no reason to think it is a biased sample if we assume there is no correlation between GPS precision and clustering inefficiency. Therefore, the results should hold for the entirety of the clusters, and, we conjecture, for other datasets too.
